\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2019-05-17 paper/tables/stmTopWords120_2.tex
new structure
new results

% Sun Aug  5 19:55:00 2018

@@

 34 & \cellcolor{white}plan & \cellcolor{white}planning & \cellcolor{white}comprehensive & \cellcolor{white}master & \cellcolor{white}review & \cellcolor{white}amendment & \mybar{42} \\ 

@@

\caption{Top words from a structural topic model with 120 topics (second 60 topics displayed here) and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics.} 

>>>>

% Fri Aug 10 15:26:58 2018

@@

@@

\caption{OLD: Top words from a structural topic model with 120 topics (second 60 topics displayed here) and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics.} 
\label{tabSTMtopwords120_2}

### 2019-05-17 paper/tables/stmTopWords60.tex
fixed a small problem with the tex table labels and renamed some stuff for more sensible file names and table labels
new results

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Fri Aug  3 14:57:28 2018

@@

 43 & \cellcolor{red!50}fun & \cellcolor{red!50}player & \cellcolor{red!50}dream & \cellcolor{red!50}celebration & \cellcolor{red!50}favorite & \cellcolor{red!50}blog & \mybar{3460} \\ 
    5 & \cellcolor{red!30}please & \cellcolor{red!30}email & \cellcolor{red!30}contact & \cellcolor{red!30}copy & \cellcolor{red!30}mail & \cellcolor{red!30}click & \mybar{201} \\ 
   42 & \cellcolor{red!20}breastfeed & \cellcolor{red!20}vaccine & \cellcolor{red!20}infection & \cellcolor{red!20}symptom & \cellcolor{red!20}asthma & \cellcolor{red!20}mosquito & \mybar{2497} \\ 
   17 & \cellcolor{red!20}alarm & \cellcolor{red!20}disaster & \cellcolor{red!20}fire & \cellcolor{red!20}rescue & \cellcolor{red!20}preparedness & \cellcolor{red!20}evacuation & \mybar{989} \\ 
   53 & \cellcolor{red!20}drinking & \cellcolor{red!20}wastewater & \cellcolor{red!20}water & \cellcolor{red!20}pipeline & \cellcolor{red!20}pump & \cellcolor{red!20}disinfection & \mybar{461} \\ 
   50 & \cellcolor{red!20}buffalo & \cellcolor{red!20}news & \cellcolor{red!20}honor & \cellcolor{red!20}warren & \cellcolor{red!20}announce & \cellcolor{red!20}lovely & \mybar{1106} \\ 
   52 & \cellcolor{red!20}reappoints & \cellcolor{red!20}digest & \cellcolor{red!20}cat & \cellcolor{red!20}leg & \cellcolor{red!20}legislator & \cellcolor{red!20}sander & \mybar{997} \\ 
   33 & \cellcolor{red!20}really & \cellcolor{red!20}think & \cellcolor{red!20}something & \cellcolor{red!20}thing & \cellcolor{red!20}somebody & \cellcolor{red!20}anybody & \mybar{1873} \\ 
   44 & \cellcolor{red!10}shall & \cellcolor{red!10}herein & \cellcolor{red!10}forth & \cellcolor{red!10}deem & \cellcolor{red!10}thereof & \cellcolor{red!10}pursuant & \mybar{405} \\ 
    8 & \cellcolor{red!10}invoice & \cellcolor{red!10}card & \cellcolor{red!10}amt & \cellcolor{red!10}filer & \cellcolor{red!10}debit & \cellcolor{red!10}officeholder & \mybar{527} \\ 
   26 & \cellcolor{red!10}fee & \cellcolor{red!10}charge & \cellcolor{red!10}billing & \cellcolor{red!10}per & \cellcolor{red!10}meter & \cellcolor{red!10}monthly & \mybar{233} \\ 
    2 & \cellcolor{red!10}yon & \cellcolor{red!10}borough & \cellcolor{red!10}comm & \cellcolor{red!10}gen & \cellcolor{red!10}sou & \cellcolor{red!10}spec & \mybar{709} \\ 
   49 & \cellcolor{red!10}bin & \cellcolor{red!10}recycling & \cellcolor{red!10}garbage & \cellcolor{red!10}recyclables & \cellcolor{red!10}recyclable & \cellcolor{red!10}bag & \mybar{1791} \\ 
    7 & \cellcolor{red!10}energy & \cellcolor{red!10}garland & \cellcolor{red!10}renewable & \cellcolor{red!10}solar & \cellcolor{red!10}electricity & \cellcolor{red!10}climate & \mybar{742} \\ 
   23 & \cellcolor{red!10}bid & \cellcolor{red!10}proposer & \cellcolor{red!10}bidder & \cellcolor{red!10}contractor & \cellcolor{red!10}subcontractor & \cellcolor{red!10}contract & \mybar{447} \\ 
   57 & \cellcolor{red!10}duct & \cellcolor{red!10}conduit & \cellcolor{red!10}bolt & \cellcolor{red!10}splice & \cellcolor{red!10}valve & \cellcolor{red!10}fitting & \mybar{1373} \\ 
   13 & \cellcolor{red!10}server & \cellcolor{red!10}wireless & \cellcolor{red!10}software & \cellcolor{red!10}telecommunication & \cellcolor{red!10}subscriber & \cellcolor{red!10}desktop & \mybar{1092} \\ 
   54 & \cellcolor{red!10}motion & \cellcolor{red!10}adjourn & \cellcolor{red!10}second & \cellcolor{red!10}unanimously & \cellcolor{red!10}ayes & \cellcolor{red!10}carry & \mybar{474} \\ 
    1 & \cellcolor{red!10}storm & \cellcolor{red!10}runoff & \cellcolor{red!10}infiltration & \cellcolor{red!10}discharge & \cellcolor{red!10}drainage & \cellcolor{red!10}drain & \mybar{516} \\ 
   38 & \cellcolor{red!10}youth & \cellcolor{red!10}student & \cellcolor{red!10}parent & \cellcolor{red!10}teacher & \cellcolor{red!10}immigrant & \cellcolor{red!10}literacy & \mybar{714} \\ 
   35 & \cellcolor{red!10}artist & \cellcolor{red!10}rouge & \cellcolor{red!10}baton & \cellcolor{red!10}art & \cellcolor{red!10}artwork & \cellcolor{red!10}exhibition & \mybar{1632} \\ 
   59 & \cellcolor{red!10}sampling & \cellcolor{red!10}sample & \cellcolor{red!10}analytical & \cellcolor{red!10}concentration & \cellcolor{red!10}hydrocarbon & \cellcolor{red!10}toxicity & \mybar{1241} \\ 
    3 & \cellcolor{red!10}portfolio & \cellcolor{red!10}yield & \cellcolor{red!10}jun & \cellcolor{red!10}maturity & \cellcolor{red!10}investment & \cellcolor{red!10}rating & \mybar{544} \\ 
   45 & \cellcolor{red!10}premise & \cellcolor{red!10}licensee & \cellcolor{red!10}violation & \cellcolor{red!10}license & \cellcolor{red!10}permit & \cellcolor{red!10}inspection & \mybar{509} \\ 
    9 & \cellcolor{red!10}para & \cellcolor{red!10}persona & \cellcolor{red!10}ante & \cellcolor{red!10}horas & \cellcolor{red!10}junta & \cellcolor{red!10}largo & \mybar{1469} \\ 
   60 & \cellcolor{red!10}exhaust & \cellcolor{red!10}fugitive & \cellcolor{red!10}aircraft & \cellcolor{red!10}airport & \cellcolor{red!10}aviation & \cellcolor{red!10}diesel & \mybar{731} \\ 
   30 & \cellcolor{white}fort & \cellcolor{white}thence & \cellcolor{white}blvd & \cellcolor{white}worth & \cellcolor{white}ave & \cellcolor{white}west & \mybar{681} \\ 
   58 & \cellcolor{white}councilor & \cellcolor{white}auburn & \cellcolor{white}plain & \cellcolor{white}ward & \cellcolor{white}beech & \cellcolor{white}glen & \mybar{480} \\ 
   51 & \cellcolor{white}whereas & \cellcolor{white}councilman & \cellcolor{white}alderman & \cellcolor{white}ordain & \cellcolor{white}hereby & \cellcolor{white}resolution & \mybar{420} \\ 
   16 & \cellcolor{white}recreation & \cellcolor{white}park & \cellcolor{white}golf & \cellcolor{white}playground & \cellcolor{white}picnic & \cellcolor{white}zoo & \mybar{682} \\ 
   36 & \cellcolor{white}retiree & \cellcolor{white}retirement & \cellcolor{white}actuarial & \cellcolor{white}deductible & \cellcolor{white}dental & \cellcolor{white}pension & \mybar{470} \\ 
   27 & \cellcolor{white}exam & \cellcolor{white}incumbent & \cellcolor{white}supervise & \cellcolor{white}supervision & \cellcolor{white}examination & \cellcolor{white}knowledge & \mybar{687} \\ 
   56 & \cellcolor{white}historic & \cellcolor{white}landmark & \cellcolor{white}revival & \cellcolor{white}archaeological & \cellcolor{white}century & \cellcolor{white}historian & \mybar{2587} \\ 
   12 & \cellcolor{white}parking & \cellcolor{white}hotel & \cellcolor{white}garage & \cellcolor{white}space & \cellcolor{white}retail & \cellcolor{white}square & \mybar{321} \\ 
   41 & \cellcolor{white}tax & \cellcolor{white}exemption & \cellcolor{white}abatement & \cellcolor{white}real & \cellcolor{white}estate & \cellcolor{white}property & \mybar{310} \\ 
    4 & \cellcolor{white}facade & \cellcolor{white}awning & \cellcolor{white}porch & \cellcolor{white}roof & \cellcolor{white}balcony & \cellcolor{white}exterior & \mybar{1108} \\ 
   28 & \cellcolor{blue!10}census & \cellcolor{blue!10}population & \cellcolor{blue!10}respondent & \cellcolor{blue!10}figure & \cellcolor{blue!10}percent & \cellcolor{blue!10}margin & \mybar{541} \\ 
   18 & \cellcolor{blue!10}prune & \cellcolor{blue!10}tree & \cellcolor{blue!10}deer & \cellcolor{blue!10}forestry & \cellcolor{blue!10}shrub & \cellcolor{blue!10}bulrush & \mybar{2522} \\ 
   15 & \cellcolor{blue!10}complainant & \cellcolor{blue!10}defendant & \cellcolor{blue!10}allegation & \cellcolor{blue!10}complaint & \cellcolor{blue!10}allege & \cellcolor{blue!10}discrimination & \mybar{1384} \\ 
   20 & \cellcolor{blue!10}noise & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}adverse & \cellcolor{blue!10}significant & \cellcolor{blue!10}vibration & \mybar{325} \\ 
   14 & \cellcolor{blue!10}yes & \cellcolor{blue!10}agency & \cellcolor{blue!10}federal & \cellcolor{blue!10}recipient & \cellcolor{blue!10}compliance & \cellcolor{blue!10}entity & \mybar{205} \\ 
   46 & \cellcolor{blue!10}variance & \cellcolor{blue!10}setback & \cellcolor{blue!10}plat & \cellcolor{blue!10}zoning & \cellcolor{blue!10}yard & \cellcolor{blue!10}fence & \mybar{289} \\ 
   29 & \cellcolor{blue!10}learn & \cellcolor{blue!10}neighborhood & \cellcolor{blue!10}graffito & \cellcolor{blue!10}event & \cellcolor{blue!10}resident & \cellcolor{blue!10}online & \mybar{196} \\ 
   25 & \cellcolor{blue!10}cannabis & \cellcolor{blue!10}marijuana & \cellcolor{blue!10}senate & \cellcolor{blue!10}dispensary & \cellcolor{blue!10}ballot & \cellcolor{blue!10}cultivation & \mybar{1188} \\ 
   22 & \cellcolor{blue!10}priority & \cellcolor{blue!10}strategic & \cellcolor{blue!10}ongoing & \cellcolor{blue!10}goal & \cellcolor{blue!10}implementation & \cellcolor{blue!10}implement & \mybar{141} \\ 
    6 & \cellcolor{blue!10}project & \cellcolor{blue!10}improvement & \cellcolor{blue!10}phase & \cellcolor{blue!10}replacement & \cellcolor{blue!10}upgrade & \cellcolor{blue!10}capital & \mybar{174} \\ 
   11 & \cellcolor{blue!10}shoreline & \cellcolor{blue!10}beach & \cellcolor{blue!10}marina & \cellcolor{blue!10}coastal & \cellcolor{blue!10}waterfront & \cellcolor{blue!10}salmon & \mybar{1069} \\ 
   24 & \cellcolor{blue!10}attract & \cellcolor{blue!10}economy & \cellcolor{blue!10}workforce & \cellcolor{blue!10}innovation & \cellcolor{blue!10}sector & \cellcolor{blue!10}economic & \mybar{748} \\ 
   47 & \cellcolor{blue!10}employee & \cellcolor{blue!10}overtime & \cellcolor{blue!10}sick & \cellcolor{blue!10}wage & \cellcolor{blue!10}grievance & \cellcolor{blue!10}bargaining & \mybar{511} \\ 
   39 & \cellcolor{blue!10}tab & \cellcolor{blue!10}accessibility & \cellcolor{blue!10}mode & \cellcolor{blue!10}var & \cellcolor{blue!10}alt & \cellcolor{blue!10}false & \mybar{259} \\ 
   10 & \cellcolor{blue!10}density & \cellcolor{blue!10}village & \cellcolor{blue!10}urban & \cellcolor{blue!10}us & \cellcolor{blue!10}mixed & \cellcolor{blue!10}corridor & \mybar{358} \\ 
   37 & \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}internal & \cellcolor{blue!10}procedure & \cellcolor{blue!10}accountability & \cellcolor{blue!10}oversight & \mybar{420} \\ 
   21 & \cellcolor{blue!10}housing & \cellcolor{blue!10}affordable & \cellcolor{blue!10}homeless & \cellcolor{blue!10}homelessness & \cellcolor{blue!10}affordability & \cellcolor{blue!10}landlord & \mybar{318} \\ 
   34 & \cellcolor{blue!10}comment & \cellcolor{blue!10}draft & \cellcolor{blue!10}feedback & \cellcolor{blue!10}stakeholder & \cellcolor{blue!10}suggest & \cellcolor{blue!10}discussion & \mybar{289} \\ 
   19 & \cellcolor{blue!10}debt & \cellcolor{blue!10}bond & \cellcolor{blue!10}governmental & \cellcolor{blue!10}obligation & \cellcolor{blue!10}financial & \cellcolor{blue!10}accounting & \mybar{251} \\ 
   40 & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}lane & \cellcolor{blue!10}crosswalk & \cellcolor{blue!10}pedestrian & \cellcolor{blue!10}bicyclist & \mybar{574} \\ 
   32 & \cellcolor{blue!20}budget & \cellcolor{blue!20}revenue & \cellcolor{blue!20}expenditure & \cellcolor{blue!20}appropriation & \cellcolor{blue!20}fund & \cellcolor{blue!20}million & \mybar{242} \\ 
   48 & \cellcolor{blue!20}absent & \cellcolor{blue!20}aye & \cellcolor{blue!20}khan & \cellcolor{blue!20}nay & \cellcolor{blue!20}berry & \cellcolor{blue!20}voting & \mybar{528} \\ 
   31 & \cellcolor{blue!20}chair & \cellcolor{blue!20}agenda & \cellcolor{blue!20}commission & \cellcolor{blue!20}speaker & \cellcolor{blue!20}chairperson & \cellcolor{blue!20}committee & \mybar{314} \\ 
   55 & \cellcolor{blue!80}robbery & \cellcolor{blue!80}homicide & \cellcolor{blue!80}arrest & \cellcolor{blue!80}sergeant & \cellcolor{blue!80}suspect & \cellcolor{blue!80}burglary & \mybar{1395} \\ 

@@

\caption{Top words from a structural topic model with 60 topics and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics. Based on data preprocessed with the classifier.} 

>>>>

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Fri May 17 09:59:58 2019

@@

 49 & \cellcolor{red!50}artist & \cellcolor{red!50}fun & \cellcolor{red!50}music & \cellcolor{red!50}beginner & \cellcolor{red!50}player & \cellcolor{red!50}prize & \mybar{4565} \\ 
   46 & \cellcolor{red!40}chair & \cellcolor{red!40}subcommittee & \cellcolor{red!40}speaker & \cellcolor{red!40}agenda & \cellcolor{red!40}committee & \cellcolor{red!40}commission & \mybar{446} \\ 
   16 & \cellcolor{red!30}motion & \cellcolor{red!30}second & \cellcolor{red!30}adjourn & \cellcolor{red!30}carry & \cellcolor{red!30}unanimous & \cellcolor{red!30}chairman & \mybar{419} \\ 
   47 & \cellcolor{red!20}effluent & \cellcolor{red!20}inf & \cellcolor{red!20}eff & \cellcolor{red!20}infiltration & \cellcolor{red!20}discharge & \cellcolor{red!20}sludge & \mybar{751} \\ 
   21 & \cellcolor{red!20}everybody & \cellcolor{red!20}think & \cellcolor{red!20}something & \cellcolor{red!20}thing & \cellcolor{red!20}try & \cellcolor{red!20}want & \mybar{2609} \\ 
    2 & \cellcolor{red!20}influenza & \cellcolor{red!20}infection & \cellcolor{red!20}vaccine & \cellcolor{red!20}patient & \cellcolor{red!20}tuberculosis & \cellcolor{red!20}hepatitis & \mybar{2980} \\ 
   27 & \cellcolor{red!20}article & \cellcolor{red!20}subsection & \cellcolor{red!20}shall & \cellcolor{red!20}franchisee & \cellcolor{red!20}paragraph & \cellcolor{red!20}meaning & \mybar{658} \\ 
   30 & \cellcolor{red!20}subcontractor & \cellcolor{red!20}bid & \cellcolor{red!20}bidder & \cellcolor{red!20}proposer & \cellcolor{red!20}subcontract & \cellcolor{red!20}bidding & \mybar{512} \\ 
   12 & \cellcolor{red!10}craftsman & \cellcolor{red!10}architecture & \cellcolor{red!10}brick & \cellcolor{red!10}distinctive & \cellcolor{red!10}revival & \cellcolor{red!10}storefront & \mybar{1731} \\ 
   24 & \cellcolor{red!10}mail & \cellcolor{red!10}fax & \cellcolor{red!10}application & \cellcolor{red!10}click & \cellcolor{red!10}applicant & \cellcolor{red!10}copy & \mybar{367} \\ 
   34 & \cellcolor{red!10}playground & \cellcolor{red!10}recreation & \cellcolor{red!10}picnic & \cellcolor{red!10}park & \cellcolor{red!10}restroom & \cellcolor{red!10}zoo & \mybar{546} \\ 
   19 & \cellcolor{red!10}setback & \cellcolor{red!10}variance & \cellcolor{red!10}zoning & \cellcolor{red!10}height & \cellcolor{red!10}yard & \cellcolor{red!10}accessory & \mybar{453} \\ 
   26 & \cellcolor{red!10}mesa & \cellcolor{red!10}canyon & \cellcolor{red!10}via & \cellcolor{red!10}odd & \cellcolor{red!10}unidentified & \cellcolor{red!10}paradise & \mybar{1886} \\ 
   23 & \cellcolor{red!10}bag & \cellcolor{red!10}recyclable & \cellcolor{red!10}recyclables & \cellcolor{red!10}reusable & \cellcolor{red!10}vegetable & \cellcolor{red!10}bait & \mybar{2254} \\ 
   20 & \cellcolor{red!10}customer & \cellcolor{red!10}renewable & \cellcolor{red!10}efficiency & \cellcolor{red!10}energy & \cellcolor{red!10}saving & \cellcolor{red!10}conservation & \mybar{652} \\ 
   31 & \cellcolor{red!10}student & \cellcolor{red!10}teacher & \cellcolor{red!10}preschool & \cellcolor{red!10}academic & \cellcolor{red!10}kindergarten & \cellcolor{red!10}youth & \mybar{855} \\ 
   28 & \cellcolor{red!10}garland & \cellcolor{red!10}assoc & \cellcolor{red!10}association & \cellcolor{red!10}firefighter & \cellcolor{red!10}duke & \cellcolor{red!10}xerox & \mybar{480} \\ 
   50 & \cellcolor{red!10}trench & \cellcolor{red!10}manhole & \cellcolor{red!10}ductile & \cellcolor{red!10}excavation & \cellcolor{red!10}pipe & \cellcolor{red!10}grout & \mybar{1436} \\ 
   32 & \cellcolor{red!10}canceled & \cellcolor{red!10}dwelling & \cellcolor{red!10}suite & \cellcolor{red!10}ave & \cellcolor{red!10}tad & \cellcolor{red!10}alteration & \mybar{491} \\ 
   51 & \cellcolor{red!10}vent & \cellcolor{red!10}combustible & \cellcolor{red!10}flammable & \cellcolor{red!10}egress & \cellcolor{red!10}ceiling & \cellcolor{red!10}extinguisher & \mybar{1160} \\ 
   44 & \cellcolor{red!10}findings & \cellcolor{red!10}tank & \cellcolor{red!10}string & \cellcolor{red!10}carcinogen & \cellcolor{red!10}lust & \cellcolor{red!10}sic & \mybar{255} \\ 
   17 & \cellcolor{red!10}portfolio & \cellcolor{red!10}micron & \cellcolor{red!10}maturity & \cellcolor{red!10}treasury & \cellcolor{red!10}yield & \cellcolor{red!10}investment & \mybar{538} \\ 
   48 & \cellcolor{red!10}contributor & \cellcolor{red!10}filer & \cellcolor{red!10}officeholder & \cellcolor{red!10}political & \cellcolor{red!10}rouge & \cellcolor{red!10}payee & \mybar{293} \\ 
    5 & \cellcolor{red!10}draft & \cellcolor{red!10}comment & \cellcolor{red!10}review & \cellcolor{red!10}revision & \cellcolor{red!10}clarify & \cellcolor{red!10}process & \mybar{356} \\ 
   37 & \cellcolor{red!10}endorsed & \cellcolor{red!10}endorse & \cellcolor{red!10}rescue & \cellcolor{red!10}assistant & \cellcolor{red!10}analyst & \cellcolor{red!10}technician & \mybar{355} \\ 
    9 & \cellcolor{red!10}trust & \cellcolor{red!10}revocable & \cellcolor{red!10}planned & \cellcolor{red!10}mfr & \cellcolor{red!10}apportionment & \cellcolor{red!10}exhibit & \mybar{361} \\ 
    8 & \cellcolor{red!10}imp & \cellcolor{red!10}assessor & \cellcolor{red!10}taxpayer & \cellcolor{red!10}petition & \cellcolor{red!10}preliminary & \cellcolor{red!10}determination & \mybar{91} \\ 
   40 & \cellcolor{white}amt & \cellcolor{white}invoice & \cellcolor{white}acct & \cellcolor{white}exp & \cellcolor{white}unencumbered & \cellcolor{white}encumbrance & \mybar{116} \\ 
   57 & \cellcolor{white}councilman & \cellcolor{white}introduced & \cellcolor{white}alderman & \cellcolor{white}whereas & \cellcolor{white}resolved & \cellcolor{white}councilwoman & \mybar{615} \\ 
   11 & \cellcolor{white}obesity & \cellcolor{white}sugary & \cellcolor{white}epidemic & \cellcolor{white}drink & \cellcolor{white}calorie & \cellcolor{white}sensible & \mybar{96} \\ 
   15 & \cellcolor{white}credit & \cellcolor{white}docket & \cellcolor{white}app & \cellcolor{white}post & \cellcolor{white}download & \cellcolor{white}month & \mybar{61} \\ 
    3 & \cellcolor{white}wetland & \cellcolor{white}specie & \cellcolor{white}species & \cellcolor{white}vernal & \cellcolor{white}ecological & \cellcolor{white}riparian & \mybar{2293} \\ 
   29 & \cellcolor{blue!10}margin & \cellcolor{blue!10}error & \cellcolor{blue!10}disability & \cellcolor{blue!10}speak & \cellcolor{blue!10}employed & \cellcolor{blue!10}language & \mybar{180} \\ 
   43 & \cellcolor{white}medicare & \cellcolor{white}payroll & \cellcolor{white}blanket & \cellcolor{white}contractual & \cellcolor{white}undistributed & \cellcolor{white}dept & \mybar{322} \\ 
   42 & \cellcolor{white}incumbent & \cellcolor{white}prep & \cellcolor{white}batch & \cellcolor{white}qualifier & \cellcolor{white}analytical & \cellcolor{white}examination & \mybar{1091} \\ 
   55 & \cellcolor{blue!10}taxable & \cellcolor{blue!10}deed & \cellcolor{blue!10}res & \cellcolor{blue!10}homestead & \cellcolor{blue!10}value & \cellcolor{blue!10}book & \mybar{87} \\ 
   22 & \cellcolor{blue!10}allocation & \cellcolor{blue!10}subtotal & \cellcolor{blue!10}admin & \cellcolor{blue!10}cost & \cellcolor{blue!10}yon & \cellcolor{blue!10}allocate & \mybar{190} \\ 
   25 & \cellcolor{blue!10}mitigation & \cellcolor{blue!10}impact & \cellcolor{blue!10}significant & \cellcolor{blue!10}adverse & \cellcolor{blue!10}environmental & \cellcolor{blue!10}measure & \mybar{217} \\ 
   56 & \cellcolor{blue!10}savings & \cellcolor{blue!10}neighborhood & \cellcolor{blue!10}village & \cellcolor{blue!10}excise & \cellcolor{blue!10}ltd & \cellcolor{blue!10}matrix & \mybar{131} \\ 
   33 & \cellcolor{blue!10}thence & \cellcolor{blue!10}east & \cellcolor{blue!10}south & \cellcolor{blue!10}corner & \cellcolor{blue!10}west & \cellcolor{blue!10}avenue & \mybar{340} \\ 
    7 & \cellcolor{blue!10}fugitive & \cellcolor{blue!10}bio & \cellcolor{blue!10}emission & \cellcolor{blue!10}coal & \cellcolor{blue!10}unmitigated & \cellcolor{blue!10}exhaust & \mybar{773} \\ 
   18 & \cellcolor{blue!10}perm & \cellcolor{blue!10}queue & \cellcolor{blue!10}delay & \cellcolor{blue!10}peak & \cellcolor{blue!10}adj & \cellcolor{blue!10}flt & \mybar{187} \\ 
   54 & \cellcolor{blue!10}license & \cellcolor{blue!10}licensee & \cellcolor{blue!10}citation & \cellcolor{blue!10}tow & \cellcolor{blue!10}fee & \cellcolor{blue!10}taxicab & \mybar{710} \\ 
    6 & \cellcolor{blue!10}race & \cellcolor{blue!10}householder & \cellcolor{blue!10}islander & \cellcolor{blue!10}census & \cellcolor{blue!10}occupied & \cellcolor{blue!10}female & \mybar{160} \\ 
   60 & \cellcolor{blue!10}bicycle & \cellcolor{blue!10}bike & \cellcolor{blue!10}pedestrian & \cellcolor{blue!10}route & \cellcolor{blue!10}sidewalk & \cellcolor{blue!10}bicyclist & \mybar{561} \\ 
   14 & \cellcolor{blue!10}accomplishment & \cellcolor{blue!10}grantee & \cellcolor{blue!10}narrative & \cellcolor{blue!10}outcome & \cellcolor{blue!10}grant & \cellcolor{blue!10}recipient & \mybar{255} \\ 
   53 & \cellcolor{blue!10}applied & \cellcolor{blue!10}col & \cellcolor{blue!10}dist & \cellcolor{blue!10}occupancy & \cellcolor{blue!10}monoxide & \cellcolor{blue!10}valuation & \mybar{128} \\ 
    4 & \cellcolor{blue!10}audit & \cellcolor{blue!10}auditor & \cellcolor{blue!10}procedure & \cellcolor{blue!10}timely & \cellcolor{blue!10}implemented & \cellcolor{blue!10}oversight & \mybar{472} \\ 
   35 & \cellcolor{blue!10}redemption & \cellcolor{blue!10}bond & \cellcolor{blue!10}increment & \cellcolor{blue!10}obligation & \cellcolor{blue!10}proceeds & \cellcolor{blue!10}lease & \mybar{339} \\ 
   39 & \cellcolor{blue!10}downtown & \cellcolor{blue!10}mixed & \cellcolor{blue!10}retail & \cellcolor{blue!10}waterfront & \cellcolor{blue!10}orient & \cellcolor{blue!10}density & \mybar{419} \\ 
   10 & \cellcolor{blue!10}grievance & \cellcolor{blue!10}deductible & \cellcolor{blue!10}coinsurance & \cellcolor{blue!10}dependent & \cellcolor{blue!10}employee & \cellcolor{blue!10}copay & \mybar{583} \\ 
   38 & \cellcolor{blue!10}para & \cellcolor{blue!10}persona & \cellcolor{blue!10}horas & \cellcolor{blue!10}bud & \cellcolor{blue!10}contracted & \cellcolor{blue!10}ante & \mybar{1334} \\ 
   36 & \cellcolor{blue!10}respondent & \cellcolor{blue!10}compare & \cellcolor{blue!10}figure & \cellcolor{blue!10}trend & \cellcolor{blue!10}appendix & \cellcolor{blue!10}satisfied & \mybar{696} \\ 
   45 & \cellcolor{blue!10}governmental & \cellcolor{blue!10}asset & \cellcolor{blue!10}actuarial & \cellcolor{blue!10}liability & \cellcolor{blue!10}financial & \cellcolor{blue!10}statement & \mybar{235} \\ 
   41 & \cellcolor{blue!20}complainant & \cellcolor{blue!20}allegation & \cellcolor{blue!20}defendant & \cellcolor{blue!20}offender & \cellcolor{blue!20}commander & \cellcolor{blue!20}complaint & \mybar{1695} \\ 
   52 & \cellcolor{blue!20}homeless & \cellcolor{blue!20}homelessness & \cellcolor{blue!20}affordable & \cellcolor{blue!20}supportive & \cellcolor{blue!20}housing & \cellcolor{blue!20}affordability & \mybar{394} \\ 
   58 & \cellcolor{blue!20}budget & \cellcolor{blue!20}revenue & \cellcolor{blue!20}adopted & \cellcolor{blue!20}balance & \cellcolor{blue!20}transfer & \cellcolor{blue!20}expenditure & \mybar{176} \\ 
   13 & \cellcolor{blue!20}initiative & \cellcolor{blue!20}outreach & \cellcolor{blue!20}strategy & \cellcolor{blue!20}leadership & \cellcolor{blue!20}engagement & \cellcolor{blue!20}focus & \mybar{502} \\ 
    1 & \cellcolor{blue!30}absent & \cellcolor{blue!30}preside & \cellcolor{blue!30}authorize & \cellcolor{blue!30}ordained & \cellcolor{blue!30}int & \cellcolor{blue!30}tag & \mybar{377} \\ 
   59 & \cellcolor{blue!80}burglary & \cellcolor{blue!80}robbery & \cellcolor{blue!80}theft & \cellcolor{blue!80}homicide & \cellcolor{blue!80}murder & \cellcolor{blue!80}gunshot & \mybar{945} \\ 

@@

\caption{Top words from a structural topic model with 60 topics and FREX scoring. Colors depict partisanship based on coefficient size. White cells are non-significant topics.} 
\label{tabSTMtopwords60}
